---
title: "1109_linear_models"
author: "Ze Li"
date: "2023-11-09"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(tidyverse)
library(p8105.datasets)
```

## Load and clean the Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(
    price, stars, borough = neighbourhood_group, 
    neighbourhood, room_type) |> 
  filter(borough != "Staten Island")

```


Let's fit a model!!

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars + borough, data = _)
```


Let's look at the `fit`

```{r}
fit
summary(fit)
summary(fit)$coef
coef(fit)
# fitted.values(fit)
```

tidy up the output instead

```{r}
fit |> 
  broom::glance()
```


tidy up the coefficients

```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)
```

## Fit another model


```{r}
fit = 
  nyc_airbnb |> 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  ) |> 
  lm(price ~ stars + borough + room_type, data = _)

fit |> 
  broom::tidy()
```


## Quick look at diagnostics

```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin() 

nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point() 

```


## Hypothesis test for categorical predictor

fit a "null" and "alternative" model

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alternative = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alternative) |> 
  broom::tidy()

```



## Borough-level differences

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars * borough + room_type * borough, data = _)

fit |> 
  broom::tidy()
```



```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data = df)
}

nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, airbnb_lm),
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)


```

same thing but just a little different


```{r}
nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)
```



## Homicides in Baltimore

```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)
  ) |> 
  select(resolved, victim_age, victim_race, victim_sex)
```


fitting a logistic regression

```{r}
fit_logistic = 
  baltimore_df |> 
  glm(
    resolved ~ victim_age + victim_race + victim_sex, 
    data = _, 
    family = binomial())
```

look at model results

```{r}
fit_logistic |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |> 
  select(term, estimate, OR)
```


```{r}
baltimore_df |> 
  count(victim_race)

```
