---
title: "1116_bootstrapping"
author: "Ze Li"
date: "2023-11-16"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(tidyverse)
library(p8105.datasets)
library(modelr)

set.seed(1)
```



## Generate a relevant example


```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1), 
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = 
  sim_df_const |> 
  mutate(
    error = error * .75 * x,
    y = 2 + 3 * x + error
  )

sim_df_nonconst |> 
  ggplot(aes(x = x, y = y)) + geom_point()


```


fit some linear models

```{r}
sim_df_const |> 
  lm(y ~ x, data = _) |> 
  broom::tidy()

sim_df_nonconst |> 
  lm(y ~ x, data = _) |> 
  broom::tidy()

```


## Draw and analyze a bootstrap sample

Start with a lil function

```{r}
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE)
  
}
```

Let's see how this works

```{r}
sim_df_nonconst |> 
  boot_sample() |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) + 
  stat_smooth(method = "lm")
```


## Draw a lot of samples and analyze them


```{r}
boot_straps = 
  tibble(strap_number = 1:1000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(sim_df_nonconst))
  )

boot_straps |> 
  pull(strap_sample) |> 
  nth(2) |> 
  arrange(x)
```

Now do the `lm` fit.

```{r}
boot_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(y ~ x, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)
```


try to summarize these results -- get a bootstrap SE

```{r}
boot_results |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )
```

look at the distribution

```{r}
boot_results |> 
  filter(term == "x") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()
```



can I construct a CI

```{r}
boot_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```



## Airbnb

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group
  ) |> 
  filter(borough != "Staten Island") |> 
  drop_na(price, stars) |> 
  select(price, stars, room_type, borough)

```

let's fit a regression of `price` on other variables and look at residuals


```{r}
airbnb_fit = 
  nyc_airbnb |> 
  lm(price ~ stars + room_type + borough, data = _)
```


residuals!!

```{r}
nyc_airbnb |> 
  modelr::add_residuals(airbnb_fit) |> 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point()
```

run a bootstrap on this whole thing to get estimates for the effect of `stars` on `price`

```{r}
manhattan_df = 
  nyc_airbnb |> 
  filter(borough == "Manhattan")


boot_results = 
  tibble(strap_number = 1:1000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(manhattan_df)),
    models = map(strap_sample, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results)

boot_results |> 
  filter(term == "stars") |> 
  ggplot(aes(x = estimate)) +
  geom_density()
```
