---
title: "writing_functions"
author: "Ze Li"
date: "2023-11-08"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(tidyverse)
library(rvest)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```

### Z score function

Z scores subtract the mean and divide by the sd. 

```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```

Compute Z scores for `x_vec`.

```{r}
(x_vec - mean(x_vec)) / sd(x_vec)
```

Write a function to do this!

```{r}
z_score = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z scores")
  }
  
  z = (x - mean(x)) / sd(x)
  
  z
  
}
```

Check that this works.

```{r}
z_score(x = x_vec)

z_score(x = rnorm(10, mean = 5))
```

Keep checking.

```{r, error = TRUE}
z_score(x = 3)

z_score(c("my", "name", "is", "jeff"))

z_score(c(TRUE, TRUE, FALSE, TRUE))

z_score(iris)
```

### Multiple outputs.

Write a function that returns the mean and sd from a sample of numbers.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z scores")
  }

  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Double check I did this right ..

```{r}
mean_and_sd(x_vec)
```

### Start getting means and sds 

```{r}

x_vec = rnorm(n = 30, mean = 5, sd = .5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)



```

Let's write a function that uses `n`, a true mean, and true SD as inputs. 

```{r}
sim_mean_sd = function(n_obs, mu = 5, sigma = 1) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
  )
  
}

sim_mean_sd(n_obs = 3000, mu = 50)

sim_mean_sd(12, 24, 4)
```

